---
title: "BART_example_NHANES"
format: html
editor: visual
---

```{r}
#| include: false
library(here)
source(here("R/library_packages.R"))
#source(here::here("R/load_and_select_data_NHANES.R"))
```
```{r}
#| include: false
data_dum <- load(here("data-raw/cvd.rda"))
names(cvd) <- tolower(names(cvd))
cvd$sex_num <- as.numeric(cvd$sex)-1
data_cvd <- cvd %>%
    select(sex_num, age, bmi, waist, sbp, dbp, hdlc,  hba1c) # add t2d  smoke, drink,
str(data_cvd)
```

**Predictors included for determining HbA1c**

```{r}
#| echo: false
set.seed(321)
data2 <- as.data.frame(na.omit(data_cvd))
data2 <- data2 %>% 
    sample_n(1000, replace = FALSE)

predictors <- data2 %>% 
    select(-(hba1c))
names(predictors)
outcome <- data2$hba1c
```

**BART model with 100 burn in, 20 trees, 300 intereations**

```{r}
set.seed(321)
bartModel <- wbart(x.train = predictors,
                   y.train = outcome,
                   nskip = 100,
                   ndpost = 300,
                   nkeeptreedraws = 300,
                   ntree = 20)
btt <- extractTreeData(model = bartModel, data = data2)
```

**Linear regression as reference**
```{r}
#| include: false
lin_reg <- lm(hba1c ~ sex_num + age + bmi + waist + sbp + dbp + hdlc, data = data2) # + smoke + drink
    
summary(lin_reg)
```

**Extracting tree data and viewving the counts of included predictors**

```{r}
vimpData <- viviBart(treeData = btt, combineFact = FALSE, out = 'vimp')
vimpData[,1:3]
sum(vimpData[,2])
```

**Ranking of the predictors**

```{r}
vimpPlot(treeData = btt, combineFact = FALSE)
```

**Exploring a random selected tree structure**

```{r}
plotTree(treeData = btt, treeNo = 12, iter = 100, plotType = "dendrogram")
plotTree(treeData = btt, treeNo = 1, iter = 1, plotType = "icicle")
```

**Tree structures in tree number 20**

```{r}
plotAllTrees(treeData = btt, treeNo = 20)
```

**Top 10 most common tree stuctures**

```{r}
treeBarPlot(treeData = btt, topTrees = 10, iter = NULL, treeNo = NULL)
```

```{r}
#localProcedure(model = bartModel,
 #              data = data2,
  #             numRep = 5,
   #            numTreesRep = 5,
    #           alpha = 0.5,
     #          shift = FALSE)
```

```{r}
stdMat <- viviBartMatrix(btt,
                          type = 'standard',
                          metric = 'propMean')
```

**Interactions between predictors**

```{r}
viviBartPlot(stdMat, impLims = c(0, 0.16), angle = 90)
```

**Diagnogsis of model**

```{r}
bartDiag(model = bartModel, response = outcome, burnIn = 100, data = data2)
```


